---
title: "Variable Selection"
author: "Daniel Chen"
date: "November 14, 2017"
output: 
  html_document: 
    df_print: kable
    number_sections: yes
    theme: paper
    toc: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, size = "small")
knitr::opts_knit$set(root.dir = '../../')
```

```{r}
library(forcats)
library(useful)
library(glmnetUtils)
library(glmnet)

rm(list = ls())

df <- readRDS('./data/subset_recode.RDS')

```

```{r}
source('./analysis/chendaniely/model_utils.R')
```


# Reference Values

```{r}
# lapply(lapply(df, levels), '[[', 1)
```

```{r}
# response variable levels
levels(df$Q13)
```

# Subset response variables

```{r}
never_every <- df[df$Q13 %in% c('Yes, every year', 'No, never'), ]
never_every$Q13 <- droplevels(never_every$Q13)
never_every$Q13 <- fct_relevel(never_every$Q13, 'No, never', after = 0L)
table(never_every$Q13, useNA = 'always')
levels(never_every$Q13)

testthat::expect_equal(levels(never_every$Q13)[1], "No, never")
```


```{r}
never_some <- df[df$Q13 %in% c('Yes, some years', 'No, never'), ]
never_some$Q13 <- droplevels(never_some$Q13)
never_some$Q13 <- fct_relevel(never_some$Q13, 'No, never', after = 0L)
table(never_some$Q13, useNA = 'always')
levels(never_some$Q13)

testthat::expect_equal(levels(never_some$Q13)[1], "No, never")
```

```{r}
never_someevery <- df[df$Q13 %in% c('Yes, every year', 'Yes, some years', 'No, never'), ]
never_someevery$Q13_nv_se <- as.character(never_someevery$Q13)

never_someevery$Q13_nv_se <- sapply(X = never_someevery$Q13_nv_se, FUN = recode_never_someevery)
never_someevery$Q13_nv_se <- as.factor(never_someevery$Q13_nv_se)
never_someevery$Q13_nv_se <- fct_relevel(never_someevery$Q13_nv_se, 'No, never', after = 0L)
table(never_someevery$Q13_nv_se, never_someevery$Q13,useNA = 'always')

levels(never_someevery$Q13_nv_se)
testthat::expect_equal(levels(never_someevery$Q13_nv_se)[1], "No, never")

never_someevery$Q13 <- never_someevery$Q13_nv_se
testthat::expect_equal(levels(never_someevery$Q13)[1], "No, never")
```

```{r}
some_every <- df[df$Q13 %in% c('Yes, some years', 'Yes, every year'), ]
some_every$Q13 <- droplevels(some_every$Q13)
some_every$Q13 <- fct_relevel(some_every$Q13, 'Yes, some years', after = 0L)
table(some_every$Q13, useNA = 'always')
levels(some_every$Q13)

testthat::expect_equal(levels(some_every$Q13)[1], "Yes, some years")
```

# Save out data

```{r}
save(never_every, never_some, never_someevery, some_every, file = 'data/model_dataframes.RData')
```


# LASSO

Use LASSO to fit a model to use as a variable selection method


## Never Every

```{r}
x  <- build.x(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
               PPMSACAT + PPREG4 + work - 1,
             data = never_every, contrasts = FALSE)
y <- build.y(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
               PPMSACAT + PPREG4 + work,
             data = never_every)

never_every_cv <- cv.glmnet(x = x, y = y, family = "binomial", nfolds = 10, weights = never_every$weight)
```

```{r}
plot(never_every_cv)
```

```{r}
# coef(never_every_cv, s = 'lambda.min')
```

## Never Some

```{r}
x  <- build.x(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
               PPMSACAT + PPREG4 + work - 1,
             data = never_some, contrasts = FALSE)
y <- build.y(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
               PPMSACAT + PPREG4 + work,
             data = never_some)

never_some_cv <- cv.glmnet(x = x, y = y, family = "binomial", nfolds = 10, weights = never_some$weight)
```

```{r}
plot(never_some_cv)
```

```{r}
# coef(never_some_cv, s = 'lambda.min')
```

## Never SomeEvery

```{r}
x  <- build.x(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
               PPMSACAT + PPREG4 + work - 1,
             data = never_someevery, contrasts = FALSE)
y <- build.y(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
               PPMSACAT + PPREG4 + work,
             data = never_someevery)

never_someevery_cv <- cv.glmnet(x = x, y = y, family = "binomial", nfolds = 10, weights = never_someevery$weight)
```

```{r}
plot(never_someevery_cv)
```

```{r}
# coef(never_someevery_cv, s = 'lambda.min')
```

## Coeff Tables

```{r}

coef_cv <- cbind(coef(never_every_cv, s = 'lambda.min'),
                 coef(never_some_cv, s = 'lambda.min'),
                 coef(never_someevery_cv, s = 'lambda.min'),
                 coef(never_every_cv, s = 'lambda.1se'),
                 coef(never_some_cv, s = 'lambda.1se'),
                 coef(never_someevery_cv, s = 'lambda.1se')
)

coef_cv <- as.data.frame(as.matrix(coef_cv))

coef_cv <- round(coef_cv, digits = 4)
coef_cv[coef_cv == 0] <- '.'

colnames(coef_cv) <- c('ne_min', 'ns_min', 'nse_min',
                    'ne_1se', 'ns_1se', 'nse_1se')

knitr::kable(coef_cv, digits = 2)
```

Using the lambda1se values we select the following demographic variables:

ppagecat
PPEDUCAT
PPETHM
income
marital
work

# Bootstrap LASSO

```{r}
total <- 100

pb <- txtProgressBar(min = 0, max = total, style = 3)

all_kept_variables <- list()

for (i in 1:total) {
  boot_never_every <- sample(x = 1:nrow(never_every), size = nrow(never_every), replace = TRUE)
  boot_never_every <- never_every[boot_never_every, ]
  
  boot_never_some <- sample(x = 1:nrow(never_some), size = nrow(never_some), replace = TRUE)
  boot_never_some <- never_some[boot_never_some, ]
  
  boot_never_someevery <- sample(x = 1:nrow(never_someevery), size = nrow(never_someevery), replace = TRUE)
  boot_never_someevery <- never_someevery[boot_never_someevery, ]
  
  
  x  <- build.x(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
                  PPMSACAT + PPREG4 + work - 1,
                data = boot_never_every, contrasts = FALSE)
  y <- build.y(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
                 PPMSACAT + PPREG4 + work,
               data = boot_never_every)
  boot_never_every_cv <- cv.glmnet(x = x, y = y, family = "binomial", nfolds = 10, weights = boot_never_every$weight)
  
  x  <- build.x(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
                  PPMSACAT + PPREG4 + work - 1,
                data = boot_never_some, contrasts = FALSE)
  y <- build.y(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
                 PPMSACAT + PPREG4 + work,
               data = boot_never_some)
  boot_never_some_cv <- cv.glmnet(x = x, y = y, family = "binomial", nfolds = 10, weights = boot_never_some$weight)
  
  x  <- build.x(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
                  PPMSACAT + PPREG4 + work - 1,
                data = boot_never_someevery, contrasts = FALSE)
  y <- build.y(Q13 ~ PPGENDER + ppagecat + PPEDUCAT + PPETHM + income + marital +
                 PPMSACAT + PPREG4 + work,
               data = boot_never_someevery)
  boot_never_someevery_cv <- cv.glmnet(x = x, y = y, family = "binomial", nfolds = 10, weights = boot_never_someevery$weight)
  
  coef_cv <- cbind(coef(boot_never_every_cv, s = 'lambda.min'),
                   coef(boot_never_some_cv, s = 'lambda.min'),
                   coef(boot_never_someevery_cv, s = 'lambda.min'),
                   coef(boot_never_every_cv, s = 'lambda.1se'),
                   coef(boot_never_some_cv, s = 'lambda.1se'),
                   coef(boot_never_someevery_cv, s = 'lambda.1se')
  )
  
  coef_cv <- as.data.frame(as.matrix(coef_cv))
  
  coef_cv <- round(coef_cv, digits = 4)
  coef_cv[coef_cv == 0] <- '.'
  
  colnames(coef_cv) <- c('ne_min', 'ns_min', 'nse_min',
                         'ne_1se', 'ns_1se', 'nse_1se')
  
  kept_variable <- coef_cv > 0
  all_kept_variables[[i]] <- kept_variable
  
  setTxtProgressBar(pb, i)
}
```

## Looking at results


### Raw Counts

```{r}
var_counts <- Reduce("+", all_kept_variables)
var_counts
```


### Counts > 50
```{r}
var_counts > 50
```

### Proportion

```{r}
var_prop <- var_counts / total
var_prop
```

### Conclusion

drop:

- PPGENDER
- PPETHM
- PPMSACAT
- marital

keep:

- ppagecat
- PPEDUCAT
- income
- PPREG4
- work
