---
title: "Model Fit"
author: "Daniel Chen"
date: "November 15, 2017"
output:
  html_document:
    df_print: kable
    number_sections: yes
    theme: paper
    toc: yes
  pdf_document:
    toc: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '../../')
rm(list = ls())
```

```{r}
library(survey)

source('analysis/chendaniely/model_utils.R')

load('data/model_dataframes.RData')


svy_never_every     <- svydesign(ids = ~1, weights = ~weight, data = never_every[!is.na(never_every$weight), ])
svy_never_some      <- svydesign(ids = ~1, weights = ~weight, data = never_some[!is.na(never_some$weight), ])
svy_never_someevery <- svydesign(ids = ~1, weights = ~weight, data = never_someevery[!is.na(never_someevery$weight), ])
svy_some_every      <- svydesign(ids = ~1, weights = ~weight, data = some_every[!is.na(some_every$weight), ])
```

# Demographic model


- ppagecat
- PPEDUCAT
- income
- PPREG4
- work

## every vs. never
```{r}
ne_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo)
```
## sometimes vs. never
```{r}
ns_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo)
```
## sometimes+every vs. never
```{r}
nse_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_someevery,
       family = quasibinomial(link = "logit"))
print_svy_mod(nse_demo)
```

# Demographic model + Belief (Q20)

## every vs. never
```{r}
ne_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief)
```

## sometimes vs. never
```{r}
ns_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief)
```

## sometimes+every vs. never
```{r}
nse_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_someevery,
       family = quasibinomial(link = "logit"))
print_svy_mod(nse_demo_belief)
```


## F statistic

```{r}
anova(ne_demo, ne_demo_belief, test = 'F')
```

```{r}
anova(ns_demo, ns_demo_belief, test = 'F')
```

```{r}
anova(nse_demo, nse_demo_belief, test = 'F')
```

## AIC/BIC

```{r}
AIC(ne_demo, ne_demo_belief)
AIC(ns_demo, ns_demo_belief)
AIC(nse_demo, nse_demo_belief)
```

```{r}
BIC(ne_demo, ne_demo_belief, maximal = ne_demo_belief)
BIC(ns_demo, ns_demo_belief, maximal = ns_demo_belief)
BIC(nse_demo, nse_demo_belief, maximal = nse_demo_belief)
```

Keep the belief variable.


# Social influence and herd immunity (Q15, 16, 17)
# Note: this is wrong, corrected in 'analysis-models.Rmd'

## every vs. never
```{r}
# ne_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q16 + Q17,
#        design = svy_never_every,
#        family = quasibinomial(link = "logit"))
# print_svy_mod(ne_demo_belief_social)
```

## sometimes vs. never
```{r}
# ns_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q16 + Q17,
#        design = svy_never_some,
#        family = quasibinomial(link = "logit"))
# print_svy_mod(ne_demo_belief_social)
```

## sometimes+every vs. never
```{r}
# nse_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q16 + Q17,
#        design = svy_never_someevery,
#        family = quasibinomial(link = "logit"))
# print_svy_mod(ne_demo_belief_social)
```

## sometimes vs. every
```{r}
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q16 + Q17,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```


## F statistic

```{r}
#anova(ne_demo_belief_social, ne_demo_belief, test = 'F')
```

```{r}
#anova(ns_demo_belief_social, ns_demo_belief, test = 'F')
```

```{r}
#anova(nse_demo_belief_social, nse_demo_belief, test = 'F')
```

## AIC/BIC

```{r}
AIC(ne_demo, ne_demo_belief, ne_demo_belief_social)
AIC(ns_demo, ns_demo_belief, ns_demo_belief_social)
AIC(nse_demo, nse_demo_belief, se_demo_belief_social)
```

```{r}
BIC(ne_demo, ne_demo_belief, ne_demo_belief_social, maximal = ne_demo_belief_social)
BIC(ns_demo, ns_demo_belief, ns_demo_belief_social, maximal = ns_demo_belief_social)
BIC(nse_demo, nse_demo_belief, se_demo_belief_social, maximal = se_demo_belief_social)
```


Drop the Social influence and herd immunity variables.

# Social influence and herd immunity Sub

## every vs. never
```{r}
ne_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q17,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief_social)
```

## sometimes vs. never
```{r}
ns_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q17,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief_social)
```

## sometimes+every vs. never
```{r}
nse_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 +Q16 + Q17,
       design = svy_never_someevery,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief_social)
```


# Cost and health insurance

## every vs. never
```{r}
ne_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14 + Q19,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief_social)
```

## sometimes vs. never
```{r}
ns_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14 + Q19,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief_social)
```

## sometimes+every vs. never
```{r}
nse_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14 + Q19,
       design = svy_never_someevery,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief_social)
```


## AIC/BIC

```{r}
AIC(ne_demo, ne_demo_belief, ne_demo_belief_social, ne_demo_belief_cost)
AIC(ns_demo, ns_demo_belief, ns_demo_belief_social, ns_demo_belief_cost)
AIC(nse_demo, nse_demo_belief, nse_demo_belief_social, nse_demo_belief_cost)
```

```{r}
BIC(ne_demo, ne_demo_belief, ne_demo_belief_cost, maximal = ne_demo_belief_cost)
BIC(ns_demo, ns_demo_belief, ns_demo_belief_cost, maximal = ns_demo_belief_cost)
BIC(nse_demo, nse_demo_belief, nse_demo_belief_cost, maximal = nse_demo_belief_cost)
```


Drop the cost variables.


# Reasons to **not** get a vaccine

Flip the response and Q18 variables

```{r}
library(forcats)
df <- readRDS('./data/subset_recode.RDS')
never_some_flipped <- df[df$Q13 %in% c('Yes, some years', 'No, never'), ]
never_some_flipped$Q13 <- droplevels(never_some$Q13)
never_some_flipped$Q13 <- fct_relevel(never_some$Q13, 'Yes, some years', after = 0L)
table(never_some_flipped$Q13, useNA = 'always')
levels(never_some_flipped$Q13)

testthat::expect_equal(levels(never_some_flipped$Q13)[1], "Yes, some years")
```

```{r}
table(never_some_flipped$Q13, never_some_flipped$Q18_1, useNA = 'always')
```


```{r}
make_no_ref <- function(dat) {
  dat <- fct_relevel(dat, "No", after = 0L)
  testthat::expect_equal(levels(dat)[1], "No")
  return(dat)
}
```


```{r}
never_some_flipped$Q18_1 <- sapply(never_some_flipped$Q18_1, make_no_ref)
never_some_flipped$Q18_2 <- sapply(never_some_flipped$Q18_2, make_no_ref)
never_some_flipped$Q18_3 <- sapply(never_some_flipped$Q18_3, make_no_ref)
never_some_flipped$Q18_4 <- sapply(never_some_flipped$Q18_4, make_no_ref)
never_some_flipped$Q18_5 <- sapply(never_some_flipped$Q18_5, make_no_ref)
never_some_flipped$Q18_6 <- sapply(never_some_flipped$Q18_6, make_no_ref)
never_some_flipped$Q18_7 <- sapply(never_some_flipped$Q18_7, make_no_ref)
never_some_flipped$Q18_8 <- sapply(never_some_flipped$Q18_8, make_no_ref)
never_some_flipped$Q18_9 <- sapply(never_some_flipped$Q18_9, make_no_ref)
never_some_flipped$Q18_10 <- sapply(never_some_flipped$Q18_10, make_no_ref)

svy_never_some_flipped <- svydesign(ids = ~1, weights = ~weight, data = never_some_flipped[!is.na(never_some_flipped$weight), ])
```

```{r}
lapply(never_some_flipped[, 37:46], table)
```


```{r}
table(df$Q18_1, df$Q13)
```

The reference response is "Yes, Sometimes."

The model is modeling NOT getting a vaccine.

## never vs. sometimes
```{r}
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + Q18_3 + Q18_4 + Q18_5 + Q18_6 + Q18_7 + Q18_8 + Q18_9 + Q18_10,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```

## 
```{r}
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + Q18_3 + Q18_4 + Q18_5 + Q18_6 + Q18_7 + Q18_8 + Q18_9 + Q18_10 + PPEDUCAT*Q20,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```

##
```{r}
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_3 + Q18_5,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```