---
title: "Models"
output:
  html_document:
    df_print: kable
    theme: paper
    toc: yes
editor_options:
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '../')
rm(list = ls())
```

```{r}
library(survey)
source('./analysis/chendaniely/model_utils.R')

# 1. run 'analysis-draft.Rmd' to get 'data_for_models.RDS'
# 2. run '01-variable_selection.Rmd' to get 'model_dataframes.RData'
# 3. run this file (modified '02-model_fit.Rmd')

load('./data/model_dataframes.RData')

svy_never_every     <- svydesign(ids = ~1, weights = ~weight, data = never_every[!is.na(never_every$weight), ])
svy_never_some      <- svydesign(ids = ~1, weights = ~weight, data = never_some[!is.na(never_some$weight), ])
svy_never_someevery <- svydesign(ids = ~1, weights = ~weight, data = never_someevery[!is.na(never_someevery$weight), ])
svy_some_every      <- svydesign(ids = ~1, weights = ~weight, data = some_every[!is.na(some_every$weight), ])
```



# 1. Demographic model (Q13 ~ Dv)

## (Dv only)
- ppagecat
- PPEDUCAT
- income
- PPREG4
- work

### Every vs. never (referent)

```{r}
# 1.1
ne_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo)
```

### Some vs. never (referent)

```{r}
# 1.1 
ns_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo)
```

```{r}
## Some + every vs. never (referent) [Remove]
# nse_demo <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work,
#        design = svy_never_someevery,
#        family = quasibinomial(link = "logit"))
# print_svy_mod(nse_demo)
```


# 1.1 Demographics + efficacy (Q20)

## (Dv, Q20)

### Every vs. never (referent)

```{r}
# 1.2
ne_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(ne_demo_belief)
```

### Some vs. never (referent)

```{r}
# 1.2
ns_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
       design = svy_never_some,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief)
```
###
```{r}
## Some + every vs. never [Remove]
# nse_demo_belief <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20,
#        design = svy_never_someevery,
#        family = quasibinomial(link = "logit"))
# print_svy_mod(nse_demo_belief)
```

**F statistic**

Every vs. never
```{r}
anova(ne_demo, ne_demo_belief, test = 'F')
```
Some vs. never
```{r}
anova(ns_demo, ns_demo_belief, test = 'F')
```
Some + every vs. never [Remove]
```{r}
#anova(nse_demo, nse_demo_belief, test = 'F')
```

**AIC/BIC**

```{r}
AIC(ne_demo, ne_demo_belief)
AIC(ns_demo, ns_demo_belief)
#AIC(nse_demo, nse_demo_belief)
```
```{r}
#BIC(ne_demo, ne_demo_belief, maximal = ne_demo_belief)
#BIC(ns_demo, ns_demo_belief, maximal = ns_demo_belief)
#BIC(nse_demo, nse_demo_belief, maximal = nse_demo_belief)
```

> Note: Keep the efficacy (Q20) variable.



# 2. Social influence (Q15, Q16, Q17)
> Note: There is no 'never' group

## (Dv, Q20, Q15,16,17)

### Every vs. some (referent) ???

```{r}
# 2.
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q15 + Q16 + Q17,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```

**F statistic**  
> Note: There is no 'never' group

```{r}
#anova(ne_demo_belief_social, ne_demo_belief, test = 'F')
```
```{r}
#anova(ns_demo_belief_social, ns_demo_belief, test = 'F')
```
```{r}
#anova(nse_demo_belief_social, nse_demo_belief, test = 'F')
```

** AIC/BIC **  
> Note: There is no 'never' group

```{r}
#AIC(ne_demo, ne_demo_belief, ne_demo_belief_social)
#AIC(ns_demo, ns_demo_belief, ns_demo_belief_social)
#AIC(nse_demo, nse_demo_belief, se_demo_belief_social)
```
```{r}
#BIC(ne_demo, ne_demo_belief, ne_demo_belief_social, maximal = ne_demo_belief_social)
#BIC(ns_demo, ns_demo_belief, ns_demo_belief_social, maximal = ns_demo_belief_social)
#BIC(nse_demo, nse_demo_belief, se_demo_belief_social, maximal = se_demo_belief_social)
```

> Note: Drop Q15.


# 2.1 Social influence subset

## (Dv, Q20, Q16)

### Every vs. some (referent)

```{r}
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q16,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```


# 2.2 Social influence subset

## (Dv, Q20, Q16,17)

### Every vs. some (referent)

```{r}
se_demo_belief_social <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q16 + Q17,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_social)
```


# 3. Cost and health insurance (Q14, Q19, Q21)
> Note: Run Q19 and Q21 separately

## (Dv, Q20, Q14)

### Every vs. some (referent)

```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```


# 3.1 Cost subset

## (Dv, Q20, Q19)

### Every vs. some (referent)

```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q19,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```


# 3.2 Cost subset

## (Dv, Q20, Q21)

### Every vs. some (referent)

```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q21,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```


# 3.3 Cost subset

## (Dv, Q20, Q14,19)

### Every vs. some (referent)

```{r}
se_demo_belief_cost <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q14 + Q19,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_demo_belief_cost)
```

**AIC/BIC**

```{r}
#AIC(ne_demo, ne_demo_belief, ne_demo_belief_social, ne_demo_belief_cost)
#AIC(ns_demo, ns_demo_belief, ns_demo_belief_social, ns_demo_belief_cost)
#AIC(nse_demo, nse_demo_belief, nse_demo_belief_social, nse_demo_belief_cost)
```
```{r}
#BIC(ne_demo, ne_demo_belief, ne_demo_belief_cost, maximal = ne_demo_belief_cost)
#BIC(ns_demo, ns_demo_belief, ns_demo_belief_cost, maximal = ns_demo_belief_cost)
#BIC(nse_demo, nse_demo_belief, nse_demo_belief_cost, maximal = nse_demo_belief_cost)
```


# 4. Barriers: Reasons to **not** get a vaccine
> Note: Flip the response and Q18 variables

```{r}
library(forcats)
df <- readRDS('./data/subset_recode.RDS')

never_some_flipped <- df[df$Q13 %in% c('Yes, some years', 'No, never'), ]
never_some_flipped$Q13 <- droplevels(never_some$Q13)
never_some_flipped$Q13 <- fct_relevel(never_some$Q13, 'Yes, some years', after = 0L)

table(never_some_flipped$Q13, useNA = 'always')
levels(never_some_flipped$Q13)

testthat::expect_equal(levels(never_some_flipped$Q13)[1], "Yes, some years")
```

```{r}
table(never_some_flipped$Q13, never_some_flipped$Q18_1, useNA = 'always')
```

```{r}
make_no_ref <- function(dat) {
  dat <- fct_relevel(dat, "No", after = 0L)
  testthat::expect_equal(levels(dat)[1], "No")
  return(dat)
}
```

```{r}
never_some_flipped$Q18_1 <- sapply(never_some_flipped$Q18_1, make_no_ref)
never_some_flipped$Q18_2 <- sapply(never_some_flipped$Q18_2, make_no_ref)
never_some_flipped$Q18_3 <- sapply(never_some_flipped$Q18_3, make_no_ref)
never_some_flipped$Q18_4 <- sapply(never_some_flipped$Q18_4, make_no_ref)
never_some_flipped$Q18_5 <- sapply(never_some_flipped$Q18_5, make_no_ref)
never_some_flipped$Q18_6 <- sapply(never_some_flipped$Q18_6, make_no_ref)
never_some_flipped$Q18_7 <- sapply(never_some_flipped$Q18_7, make_no_ref)
never_some_flipped$Q18_8 <- sapply(never_some_flipped$Q18_8, make_no_ref)
never_some_flipped$Q18_9 <- sapply(never_some_flipped$Q18_9, make_no_ref)
never_some_flipped$Q18_10 <- sapply(never_some_flipped$Q18_10, make_no_ref)

svy_never_some_flipped <- svydesign(ids = ~1, weights = ~weight, data = never_some_flipped[!is.na(never_some_flipped$weight), ])
```

```{r}
lapply(never_some_flipped[, 37:46], table)
```

```{r}
table(df$Q18_1, df$Q13)
```

> Note: The reference response is "Yes, Some years." The model is modeling NOT getting a vaccine.


## (Dv, Q18_1,2,3,4,5,6,7,8,9)

### Never vs. some (referent)

```{r}
# Barriers only
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q18_1 + Q18_2 + Q18_3 + Q18_4 + Q18_5 + Q18_6 + Q18_7 + Q18_8 + Q18_9,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```

> Note: p-value < 0.05 for Q18_1, 2, 3, 5, 8
> Only including the above Q18 subset


# 4.1 Barriers subset + efficacy (Q18, Q20)

## (Dv + Q20 + Q18_1,2,3,4,5,6,7,8,9)

### Never vs. some (referent)

```{r}
# Barriers + efficacy
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + Q18_3 + Q18_4 + Q18_5 + Q18_6 + Q18_7 + Q18_8 + Q18_9,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```


# 4.2 Barriers subset + efficacy + cost (Q18, Q20, Q19)

## (Dv + Q20 + Q19 + Q18_1,2,3,5,7,8)

### Never vs. some (referent)

```{r}
# Barriers + efficacy + cost
ns_demo_belief_barriers <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q18_1 + Q18_2 + Q18_3 + Q18_5 + Q18_7 + Q18_8 + Q19,
       design = svy_never_some_flipped,
       family = quasibinomial(link = "logit"))
print_svy_mod(ns_demo_belief_barriers)
```



# 5. Combined model

## (Dv, Q20, Q16,17, Q14,19)

### Every vs. some (referent)

```{r}
se_model <- svyglm(formula = Q13 ~ ppagecat + PPEDUCAT + income + PPREG4 + work + Q20 + Q16 + Q17 + Q14 + Q19,
       design = svy_some_every,
       family = quasibinomial(link = "logit"))
print_svy_mod(se_model)
```