---
title: "analysis draft"
output: 
  html_document:
    fig_caption: yes
    fig_height: 3
    fig_width: 6
    keep_md: yes
    theme: paper
    toc: yes
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list = ls(all.names = TRUE))
knitr::opts_knit$set(root.dir = '..')
knitr::opts_chunk$set(echo = T, cache = T, warning = F, message = F, tidy = T, size = "small")
```

```{r}
library(dplyr)
library(ggplot2)
library(gridExtra)
library(knitr)
library(rmarkdown)
library(survey)
library(tidyr)

## flu-survey/code/data_prep.R
load('./data/data_prep.RData')

## subset columns
df <- dataf[, c(1,4:27, 28:33, 92:111, 429)]
names(df)
```

```{r recode-data}
## recode variables
library(car)

## use code function for response variables
## reset the "default" level on categorical variables
code <- function(col, map, ref) {
  relevel(as.factor(map[col]), ref=ref)
}

## income - PPINCIMP
income.map <- c(rep("under $10k", 3),
                rep("$10k to $25k", 4),
                rep("$25k to $50k", 4),
                rep("$50k to $75k", 2),
                rep("$75k to $100k", 2),
                rep("$100k to $150k", 2),
                rep("over $150k", 2))
df$income <- code(dataf$PPINCIMP, income.map, "under $10k")
income.lab <- c("under $10k", "$10k to $25k", "$25k to $50k", "$50k to $75k", "$75k to $100k", "$100k to $150k", "over $150k")
df$income <- factor(df$income, levels = income.lab)

## marital status - PPMARIT
marital.map <- c("single", "partnered", "partnered", "single", "single", "single")
df$marital <- code(dataf$PPMARIT, marital.map, "single")

## employment status - PPWORK
work.map <- c(rep("unemployed", 5),
              rep("employed", 2))
df$work <- code(dataf$PPWORK, work.map, "unemployed")

## check columns
colnames(df)


saveRDS(df, file = './data/subset_recode.RDS')
```

```{r ggplot}
## ggplot templates
ptext <- theme(axis.text = element_text(size = rel(0.9)), axis.text.x = element_text(angle = 45, hjust = 1))
ptext2 <- ptext + theme(axis.text.x = element_blank())
```

```{r survey-des}
## create survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des <- svydesign(ids = ~1, weights = ~weight, data = df[!is.na(df$weight), ])
```



# Q13. Do you get the flu vaccine?

```{r}
## Q13. Do you get the flu vaccine?
q13 <- as.data.frame(svytable(~Q13 + ppagecat + PPGENDER + PPETHM + income + PPEDUCAT + work + marital, des, round = T))

# univariate
p <- ggplot(q13, aes(Q13, weight = Freq)) + ptext
p + geom_bar() + ggtitle("Q13. Do you get the flu vaccine?")

# raw count
with(df, addmargins(table(Q13)))

# weighted count
as.data.frame(svytable(~Q13, des, round = T))
```

```{r eval=FALSE, include=FALSE}
## Q13: chi-squares
svychisq(~Q13 + ppagecat, des)
#svychisq(~Q13 + ppagect4, des)
#svychisq(~Q13 + PPEDUC, des)
svychisq(~Q13 + PPEDUCAT, des)
svychisq(~Q13 + PPETHM, des)
svychisq(~Q13 + PPGENDER, des)
svychisq(~Q13 + PPHHHEAD, des)
#svychisq(~Q13 + PPHOUSE, des)
svychisq(~Q13 + income, des)
svychisq(~Q13 + marital, des)
svychisq(~Q13 + PPMSACAT, des)
svychisq(~Q13 + PPREG4, des)
svychisq(~Q13 + ppreg9, des)
svychisq(~Q13 + PPRENT, des)
svychisq(~Q13 + PPSTATEN, des)
svychisq(~Q13 + PPT01, des)
svychisq(~Q13 + PPT25, des)
svychisq(~Q13 + PPT612, des)
svychisq(~Q13 + PPT1317, des)
#svychisq(~Q13 + PPT18OV, des) #
svychisq(~Q13 + work, des)
svychisq(~Q13 + PPNET, des)
```

Significant p-values for Q13:
Age, education, ethnicity, housing type, income, marital status, metro status, region, rental status, employment status, internet 


## Ethnicity

```{r}
### Q13 and PPETHM: EXAMPLE

# chi-square: Q13 and PPETHM
svychisq(~Q13 + PPETHM, des)

# glm: Q13 and PPETHM
a <- glm(Q13 ~ PPETHM, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# unweighted table
as.data.frame(with(df, addmargins(table(PPETHM, Q13))))

# weighted proportions
(q <- svyby(~Q13, ~PPETHM, des, svymean, na.rm = T))

# plot: Q13. No, never
er <- geom_errorbar(aes(ymin = q[4] - q[7],
                        ymax = q[4] + q[7]), width = .25)
ggplot(q, aes(PPETHM, q[4])) + geom_point() + xlab("") + ylab("Q13No, never") + er + ggtitle(label = "") 
```

## Gender

```{r}
## Q13 and PPGENDER
svychisq(~Q13 + PPGENDER, des)

a <- glm(Q13 ~ PPGENDER, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# unweighted table
as.data.frame(with(df, addmargins(table(PPGENDER, Q13))))
# weighted props
(q <- svyby(~Q13, ~PPGENDER, des, svymean, na.rm = T))


# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPGENDER, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "")
```

## Age

```{r}
## Q13 and ppagecat
svychisq(~Q13 + ppagecat, des)

a <- glm(Q13 ~ ppagecat, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# weighted props
(q <- svyby(~Q13, ~ppagecat, des, svymean, na.rm = T))
# unweighted table
as.data.frame(with(df, addmargins(table(ppagecat, Q13))))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(ppagecat, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "")
```

```{r eval=FALSE, include=FALSE}
## Q13 and ppagect4
svychisq(~Q13 + ppagect4, des)

a <- glm(Q13 ~ ppagect4, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# weighted table
(q <- svyby(~Q13, ~ppagect4, des, svymean, na.rm = T))

# unweighted table
as.data.frame(with(df, addmargins(table(ppagect4, Q13))))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(ppagect4, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "")
```

## Education

```{r}
## Q13 and PPEDUCAT
svychisq(~Q13 + PPEDUCAT, des)

a <- glm(Q13 ~ PPEDUCAT, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# weighted table
(q <- svyby(~Q13, ~PPEDUCAT, des, svymean, na.rm = T))
# unweighted table
as.data.frame(with(df, addmargins(table(PPEDUCAT, Q13))))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPEDUCAT, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "")
```

## Housing type

```{r eval=FALSE, include=FALSE}
## Q13 and PPHOUSE
svychisq(~Q13 + PPHOUSE, des)

a <- glm(Q13 ~ PPHOUSE, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# weighted table
(q <- svyby(~Q13, ~PPHOUSE, des, svymean, na.rm = T))
# unweighted table
with(df, addmargins(table(Q13, PPHOUSE)))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPHOUSE, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "") 
```

## Income

```{r}
## Q13 and income
svychisq(~Q13 + income, des)

a <- glm(Q13 ~ income, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# weighted table
(q <- svyby(~Q13, ~income, des, svymean, na.rm = T))
# unweighted table
as.data.frame(with(df, addmargins(table(income, Q13))))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(income, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "") 
```

## Marital status

```{r}
## Q13 and marital
svychisq(~Q13 + marital, des)

a <- glm(Q13 ~ marital, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# unweighted table
as.data.frame(with(df, addmargins(table(marital, Q13))))
# weighted table
(q <- svyby(~Q13, ~marital, des, svymean, na.rm = T))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(marital, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "") 
```

## Metro status

```{r}
## Q13 and PPMSACAT
svychisq(~Q13 + PPMSACAT, des)

a <- glm(Q13 ~ PPMSACAT, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# unweighted table
as.data.frame(with(df, addmargins(table(PPMSACAT, Q13))))
# weighted table
(q <- svyby(~Q13, ~PPMSACAT, des, svymean, na.rm = T))


# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPMSACAT, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "")
```

## Region

```{r}
## Q13 and region4 and region9
svychisq(~Q13 + PPREG4, des)
svychisq(~Q13 + ppreg9, des)

a <- glm(Q13 ~ PPREG4, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)
b <- glm(Q13 ~ ppreg9, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(b)

# unweighted table
as.data.frame(with(df, addmargins(table(PPREG4, Q13))))
with(df, addmargins(table(Q13, ppreg9)))

# weighted table
(q <- svyby(~Q13, ~PPREG4, des, svymean, na.rm = T))
(q2 <- svyby(~Q13, ~ppreg9, des, svymean, na.rm = T))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPREG4, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "") 

er2 <- geom_errorbar(aes(ymin = q2[2] - q2[5],
                        ymax = q2[2] + q2[5]), width = .25)
ggplot(q2, aes(ppreg9, q2[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er2 + ggtitle(label = "") 
```

## Rental Status

```{r eval=FALSE, include=FALSE}
## Q13 and PPRENT
svychisq(~Q13 + PPRENT, des)

a <- glm(Q13 ~ PPRENT, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# weighted table
(q <- svyby(~Q13, ~PPRENT, des, svymean, na.rm = T))
# unweighted table
with(df, addmargins(table(Q13, PPRENT)))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPRENT, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "") 
```

## Employment status

```{r}
## Q13 and work
svychisq(~Q13 + work, des)

a <- glm(Q13 ~ work, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# unweighted table
as.data.frame(with(df, addmargins(table(work, Q13))))
# weighted table
(q <- svyby(~Q13, ~work, des, svymean, na.rm = T))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(work, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "") 
```

## Internet status

```{r}
## Q13 and PPNET
svychisq(~Q13 + PPNET, des)

a <- glm(Q13 ~ PPNET, family = quasibinomial(link = "logit"), data = df, weights = weight)
summary(a)

# unweighted table
as.data.frame(with(df, addmargins(table(PPNET, Q13))))
# weighted table
(q <- svyby(~Q13, ~PPNET, des, svymean, na.rm = T))

# plot: Yes, every year
er <- geom_errorbar(aes(ymin = q[2] - q[5],
                        ymax = q[2] + q[5]), width = .25)
ggplot(q, aes(PPNET, q[2])) + geom_point() + xlab("") + ylab("Q13Yes, every year") + er + ggtitle(label = "Internet status")
```


# Q14. How much do you pay to get an influenza vaccine?

```{r}
## Q14. How much do you pay to get an influenza vaccine?
q14 <- as.data.frame(svytable(~Q14 + Q13 + ppagecat + PPGENDER + PPETHM + PPEDUCAT, des, round = T))

# univariate
title <- ggtitle("Q14. How much do you pay to get an influenza vaccine?")
p <- ggplot(q14, aes(Q14, weight = Freq)) + ptext
p + geom_bar() + title

# counts
with(df, addmargins(table(Q14)))

# bivariate
ggplot(q14, aes(Q14, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q14 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q14')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q14) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q14')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q14, Q13)))

## drop where too few observations
#df_sub <- df_sub[!df_sub$Q14=="More than $60" & !df_sub$Q13=="No, never", ]
df_sub <- df_sub[!df_sub$Q14=="More than $60", ]
nrow(df_sub)

## drop unused levels
df_sub <- droplevels(df_sub)

## updated count
with(df_sub, addmargins(table(Q14, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des14 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
#svytable(~Q14 + Q13, des14, round = T)  # weighted counts
svyby(~Q13, ~Q14, des14, svymean, na.rm.all = T)

svychisq(~Q14 + Q13, des14)
a <- glm(Q13 ~ Q14, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```


# Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?

```{r}
## Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?
q20 <- as.data.frame(svytable(~Q20 + Q13 + ppagecat + PPGENDER + PPETHM + PPEDUCAT, des, round = T))

# univariate
title <- ggtitle("Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?")
ggplot(q20, aes(Q20, weight = Freq)) + ptext + geom_bar() + title

# counts
with(df, addmargins(table(Q20)))

# bivariate
ggplot(q20, aes(Q20, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q20 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q20')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q20) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q20')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q20, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des20 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
svyby(~Q13, ~Q20, des20, svymean, na.rm = T)

# chisq
svychisq(~Q20 + Q13, des20)
a <- glm(Q13 ~ Q20, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```


# Q15. Are you more likely to get a vaccine if others around you get a vaccine?

```{r}
## Q15. Are you more likely to get a vaccine if others around you get a vaccine?
q15 <- as.data.frame(svytable(
  ~Q15 + Q13 + PPGENDER + ppagecat + PPETHM + income + PPEDUCAT, des, round = T))

# univariate
title <- ggtitle("Q15. Are you more likely to get a vaccine if others around you get a vaccine?")
p <- ggplot(q15, aes(Q15, weight = Freq)) + ptext
p + geom_bar() + title

# bivariate
ggplot(q15, aes(Q15, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q15 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q15')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q15) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q15')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q15, Q13)))

## drop unused levels
df_sub <- droplevels(df_sub)

## updated count
with(df_sub, addmargins(table(Q15, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des15 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
#svytable(~Q15 + Q13, des15, round = T)  # weighted counts
svyby(~Q13, ~Q15, des15, svymean, na.rm.all = T)

svychisq(~Q15 + Q13, des15)
a <- glm(Q13 ~ Q15, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```

# Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?

```{r}
## Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?
q16 <- as.data.frame(svytable(
  ~Q16 + Q13 + PPGENDER + ppagecat + PPETHM + income + PPEDUCAT, des, round = T))

# univariate
title <- ggtitle("Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?")
p <- ggplot(q16, aes(Q16, weight = Freq)) + ptext
p + geom_bar() + title

# counts
with(df, addmargins(table(Q16)))

# bivariate
ggplot(q16, aes(Q16, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q16 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q16')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q16) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q16')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q16, Q13)))

## drop unused levels
df_sub <- droplevels(df_sub)

## updated count
with(df_sub, addmargins(table(Q16, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des16 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
#svytable(~Q16 + Q13, des16, round = T)  # weighted counts
svyby(~Q13, ~Q16, des16, svymean, na.rm.all = T)

svychisq(~Q16 + Q13, des16)
a <- glm(Q13 ~ Q16, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```


# Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?

```{r}
## Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?
q17 <- as.data.frame(svytable(
  ~Q17 + Q13 + PPGENDER + ppagecat + PPETHM + income + PPEDUCAT, des, round = T))

title <- ggtitle("Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?")
p <- ggplot(q17, aes(Q17, weight = Freq)) + ptext
p + geom_bar() + title

# counts
with(df, addmargins(table(Q17)))

# bivariate
ggplot(q17, aes(Q17, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q17 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q17')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q17) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q17')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q17, Q13)))

## drop unused levels
df_sub <- droplevels(df_sub)

## updated count
with(df_sub, addmargins(table(Q17, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des17 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
#svytable(~Q17 + Q13, des17, round = T)  # weighted counts
svyby(~Q13, ~Q17, des17, svymean, na.rm.all = T)

svychisq(~Q17 + Q13, des17)
a <- glm(Q13 ~ Q17, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```


# Q19. Do you have health insurance?

```{r}
## Q19. Do you have health insurance?
q19 <- as.data.frame(svytable(
  ~Q19 + Q13 + PPGENDER + ppagecat + PPETHM + income + PPEDUCAT, des, round = T))

# univariate
title <- ggtitle("Q19. Do you have health insurance?")
p <- ggplot(q19, aes(Q19, weight = Freq)) + ptext
p + geom_bar() + title

# counts
with(df, addmargins(table(Q19)))

# bivariate
ggplot(q19, aes(Q19, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q19 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q19')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q19) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q19')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q19, Q13)))

## drop unused levels
df_sub <- droplevels(df_sub)

## updated count
with(df_sub, addmargins(table(Q19, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des19 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
#svytable(~Q19 + Q13, des19, round = T)  # weighted counts
svyby(~Q13, ~Q19, des19, svymean, na.rm.all = T)

svychisq(~Q19 + Q13, des19)
a <- glm(Q13 ~ Q19, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```


# Q21. Are influenza vaccines covered by your insurance?

```{r}
## Q21. Are influenza vaccines covered by your insurance?
### subset by Q19 = Yes
q21 <- as.data.frame(svytable(~Q21 + Q13 + ppagecat + PPGENDER + PPETHM + PPEDUCAT, des, round = T))

# univariate
title <- ggtitle("Q21. How much do you pay to get an influenza vaccine?")
p <- ggplot(q21, aes(Q21, weight = Freq)) + ptext
p + geom_bar() + title

# counts
with(df, addmargins(table(Q21)))

# bivariate
ggplot(q21, aes(Q21, fill = Q13, weight = Freq)) + ptext + geom_bar() + title
```

```{r}
## Q21 by Q13: vaccination status
#head(df[c('CaseID','Q13','Q21')])
#nrow(df)

## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q21) & !is.na(df$Q13), ]
head(df_sub[c('CaseID','Q13','Q21')])
nrow(df_sub)

## count
with(df_sub, addmargins(table(Q21, Q13)))

## drop unused levels
df_sub <- droplevels(df_sub)

## updated count
with(df_sub, addmargins(table(Q21, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des21 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted table
#svytable(~Q21 + Q13, des21, round = T)  # weighted counts
svyby(~Q13, ~Q21, des21, svymean, na.rm.all = T)

svychisq(~Q21 + Q13, des21)
a <- glm(Q13 ~ Q21, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
summary(a)
```


# Q18. What are the reasons you would not get an influenza vaccine?

```{r}
## Q18. What are the reasons you would not get an influenza vaccine?
title <- ggtitle("Q18. What are the reasons you would not get an influenza vaccine?")
```

```{r}
## Q18 by Q13: vaccination status
## drop NAs from variables of interest
df_sub <- df[!is.na(df$Q18_1) & !is.na(df$Q13), ]
#head(df_sub[c('CaseID','Q13','Q18_1')])
nrow(df_sub)

## count for Q18_1
with(df_sub, addmargins(table(Q18_1, Q13)))

## drop unused levels
df_sub <- droplevels(df_sub)

## updated counts for all Q18
with(df_sub, addmargins(table(Q18_1, Q13)))
with(df_sub, addmargins(table(Q18_2, Q13)))
with(df_sub, addmargins(table(Q18_3, Q13)))
with(df_sub, addmargins(table(Q18_4, Q13)))
with(df_sub, addmargins(table(Q18_5, Q13)))
with(df_sub, addmargins(table(Q18_6, Q13)))
with(df_sub, addmargins(table(Q18_7, Q13)))
with(df_sub, addmargins(table(Q18_8, Q13)))
with(df_sub, addmargins(table(Q18_9, Q13)))

## update survey object
options(digits = 4)
options(survey.lonely.psu = "adjust")
des18 <- svydesign(ids = ~1, weights = ~weight, data = df_sub)

## weighted tables
svyby(~Q13, ~Q18_1, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_2, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_3, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_4, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_5, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_6, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_7, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_8, des18, svymean, na.rm.all = T)
svyby(~Q13, ~Q18_9, des18, svymean, na.rm.all = T)

svychisq(~Q18_9 + Q13, des18)
#a <- glm(Q13 ~ Q18_1, family = quasibinomial(link = "logit"), data = df_sub, weights = weight)
#summary(a)
```


# Regression model

```{r}
# write out data before fitting models

saveRDS(object = df, file = './data/data_for_models.RDS')
```

```{r}
# Q13
library(MASS)
library(broom)
m <- polr(Q13 ~ Q1, weights = df$weight, data = df, Hess=TRUE)
summary(m)

#exp(m$coefficients)
#coef(summary(m))

danresults <- tidy(coef(summary(m)))
danresults$OR <- exp(danresults$Value)
danresults$ORupper <- exp(danresults$Value + 1.96*danresults$Std..Error)
danresults$ORlower <- exp(danresults$Value - 1.96*danresults$Std..Error)
danresults
```

Q13. Do you get the flu vaccine?
Q14. How much do you pay to get an influenza vaccine?
Q15. Are you more likely to get a vaccine if others around you get a vaccine?
Q16. Are you more likely to get a vaccine if others around you do not get a vaccine?
Q17. Do you get a vaccine to protect yourself, protect others, or protect yourself and others?
Q18. What are the reasons you would not get an influenza vaccine?
Q19. Do you have health insurance?
Q20. How effective do you think the influenza vaccine is in protecting people from becoming sick with influenza?
Q21. Are influenza vaccines covered by your insurance?
